---
title: "HW1 document"
output: github_document
---

## Problem 1
```{r}
data("penguins", package = "palmerpenguins")

```

## Description 

This `penguins`dataset shows total collected 344 samples of penguins from 2007 to 2009 with 3 different species across different locations. This dataset also includes variables: `species`, `island`, `bill_length_mm` and`bill_ depth_mm`, `flipper_length_mm`, `body_mass_g`, `sex`, and `year`. There are total 334 `nrow` and total 8 `ncol`. The mean flipper length is 200.9152.

## Mean of flipper_length
```{r}
library(tidyverse)
mean_flipper_length = mean(pull(penguins, flipper_length_mm), na.rm=TRUE)
mean_flipper_length
```


##Scatterplot
```{r}
library(ggplot2)
library(palmerpenguins)

# Load the penguins dataset
data("penguins")

# Create a scatterplot
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

## Save image
```{r}
ggsave("penguins_scatterplot.png")
```

## Problem 2

```{r}
library(tidyverse)
example_df = tibble (
  vec_number = rnorm(10),
  vec_logical = vec_number > 0,
  char_vec = c("1","2","3","4","5","6","7","8","9","10"),
  fact_vec = factor(sample(c("level1","level2","level3"),10, replace = TRUE)))
print(example_df)
```

